Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_2_literature.tex
Rearrange figures
Add Alex' changes on releated works

Early image captioning systems mainly used an RNN architecture with a closed
vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
Attention over image patches was later introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Later improvements include giving the model the option to not
attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
generic captions with a limited vocabulary.

A more challenging task is to produce captions for news images, in which we
need to be able to generate entity names. Early non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
article and and the VGG19 representation of the image, and feed them as inputs
to an LSTM generator. However the generator still cannot produce names not
seen in training.

@@

>>>>

A large number of methods exist for generating generic image captions that
describe objects and relationships using only image information. Many of these
captioning systems use some combination of a Convolutional Neural Network
encoder and a RNN with a closed
vocabulary as a decoder~\cite{Karpathy2015DeepVA, Donahue2015LongTR,
Vinyals2015ShowAT}.
Attention over image patches was introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Many extensions to these models have been proposed such as giving
the model the option to not
attend to any image region~\cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimise for the CIDEr metric~\cite{Rennie2017SelfCriticalST,
Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
attend to \cite{Anderson2017BottomUpAT}. All of these systems generate
restricted vocabulary generic captions without considering context external to
the image.

A related task which does consider image context is news image captioning,
where the image caption is generated using the article text as context.
One key challenge of news image captioning is generating rare entity names, for
example the names of people who do not make many media appearances. Early
non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
article and and the VGG19 representation of the image, and feed them as inputs
to an LSTM generator. However the generator still cannot produce names not
seen in training.

@@

\begin{figure*}[t]
    \begin{center}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \end{center}
       \caption{Overall architecture of the model.}
    \label{fig:short}
 \end{figure*}
